
# Homework 2: "HW2_JW3597"
#### Name: Jessie Wong
#### Date: September 28, 2018

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
```

###Problem 1: 
```{r}
getwd()
# Read the csv for problem 1
nyc_transit = read_csv(file = "./data_files/NYC_Transit_Subway_Entrance_And_Exit_Data.csv")

# Cleaning the data from the CSV:

# Cleaning the variable names after import: The variable names were changed to lower snake case
nyc_transit = janitor::clean_names(nyc_transit)
names(nyc_transit)  
```

```{r}

select(nyc_transit, line, station_name, station_latitude, station_longitude, route1, route2, route3, route4, route5, route6, route7, route8, route9, route10, route11, entry, vending, entrance_type, ada)

# Converting entry variable from character to a logical variable 
nyc_transit$entry <- as.logical(recode(nyc_transit$entry, "YES" = "TRUE", "NO" = "FALSE"))
View(nyc_transit$entry)

# How many distinct stations are there?
name_line = distinct(nyc_transit, station_name, line)
nrow(name_line)

# How many stations are ADA compliant?
ada_compliant = distinct(nyc_transit, station_name, line, ada)
filter(ada_compliant, ada == "TRUE")

# What proportion of station extrances/exits without vending allow entrance?
novending_yesentry = filter(nyc_transit, vending == "NO", entry == "TRUE")
nrow(novending_yesentry)/nrow(nyc_transit)*100
```
There are 465 distinct stations. There are 84 stations that are ADA compliant. The proportion of station entrances/exits without vending allow entrace is 3.69%.

###Problem 2: 
```{r}
# read the Mr. Trash Wheel sheet
library(readxl)
trash_wheel = read_excel("./data_files/HealthyHarborWaterWheelTotals2018-7-28.xlsx", sheet = 1, range = "A2:N258")

# Variable names used in the Mr. Trash Wheel Sheet are reasonable

# Omit rows that do not include dumpster-specific data
na.omit(trash_wheel, cols  = "Dumpster")

# Round number of sports balls to the nearest integer and converts the result to an integer variable
trash_wheel$`Sports Balls Rounded` <- as.integer(trash_wheel$`Sports Balls`)

# Median value of sports balls in a dumpter in 2016
median(trash_wheel$`Sports Balls Rounded`)
```

```{r}
#Read and clean precipitation data for 2016
library(readxl)
precip2016 = read_excel("./data_files/HealthyHarborWaterWheelTotals2018-7-28.xlsx", sheet = 5)

# Omit rows without precipitation data for 2016
na.omit(precip2016, cols  = "Total")

# Adding a variable year for 2016
precip2016 = mutate(precip2016, Year = "2016")

#Read and clean precipitation data for 2017
library(readxl)
precip2017 = read_excel("./data_files/HealthyHarborWaterWheelTotals2018-7-28.xlsx", sheet = 4)

# Omit rows without precipitation data for 2017
na.omit(precip2017, cols  = "Total")

# Adding a variable year for 2017
precip2017 = mutate(precip2017, Year = "2017")

# Combine datasets and convert month to a character variable
precip2016 <- read_excel("./data_files/HealthyHarborWaterWheelTotals2018-7-28.xlsx", sheet = 5)
precip2017 <- read_excel("./data_files/HealthyHarborWaterWheelTotals2018-7-28.xlsx", sheet = 4)

totalprecip <- merge(precip2016, precip2017, all.x = TRUE, all.y = TRUE)
View(totalprecip)
```
The number of observations in both resulting datasets was 12 in each and (24 in total). The key variables included year, precipitation (in inches), and the month that the precipation occurred. The total precipation in 2017 was 32.93. The median number of sports balls in a dumpster in 2016 was 15.5. 

```{r}
install.packages("devtools")
devtools::install_github("p8105/p8105.datasets")
library(p8105.datasets)
data("brfss_smart2010")
View(brfss_smart2010)
brfss_smart2010

# Exclude variables for class, topic, question, sample size, and everything from lower confidence limit to GeoLocation / Format the Data to use appropriate variable names
library(dplyr)
select(brfss_smart2010, Year = Year, State = Locationabbr, County = Locationdesc, Response = Response, Health_Score = Data_value)

# Structure data so that values for Response (“Excellent” to “Poor”) are column names / variables which indicate the proportion of subjects with each response (which are values of Data_value in the original dataset)
mutate(brfss_smart2010, Excellent = )
mutate(brfss_smart2010, Very_Good = )
mutate(brfss_smart2010, Fair = )
mutate(brfss_smart2010, Poor = )
```
